Rising from the Ashes: How the Milky Way Got Its Scars

### 2024-04-13 paper/ms.tex
Update header and ref
Update title and abstract

%% Beginning of file 'sample631.tex'
%%
%% Modified 2021 March
%%
%% This is a sample manuscript marked up using the
%% AASTeX v6.31 LaTeX 2e macros.
%%
%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
%% (Copyright 2000-2015).  See the classfile for details.

%% AASTeX requires revtex4-1.cls and other external packages such as
%% latexsym, graphicx, amssymb, longtable, and epsf.  Note that as of 
%% Oct 2020, APS now uses revtex4.2e for its journals but remember that 
%% AASTeX v6+ still uses v4.1. All of these external packages should 
%% already be present in the modern TeX distributions but not always.
%% For example, revtex4.1 seems to be missing in the linux version of
%% TexLive 2020. One should be able to get all packages from www.ctan.org.
%% In particular, revtex v4.1 can be found at 
%% https://www.ctan.org/pkg/revtex4-1.

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%% using aastex version 6.3
\documentclass[linenumbers, twocolumn]{aastex631}

@@

\newcommand{\Msun}{\ensuremath{M_{\odot}}}
\newcommand{\yr}{\ensuremath{\textrm{yr}}}
\newcommand{\kpc}{\ensuremath{\textrm{kpc}}}
\newcommand{\pc}{\ensuremath{\textrm{pc}}}

@@

\title{Stimulated Accretion from Circumgalactic Media Interactions}

@@

\author{Federico Marinacci}
\affiliation{Department of Physics \& Astronomy `Augusto Righi', 
University of Bologna, Bologna, Italy}

@@

\author{others}

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
  It is now well-established that galaxies host extended gaseous haloes dubbed
  the circumgalactic medium (CGM) which play a critical role in receiving and
  providing gas from and to the disk. Typically metal-poor, the CGM is a major
  actor in the nuclear abundance evolution of galaxies. While aspects of
  isolated CGM, such as its rotation and multiphase nature, have been studied,
  the interaction between the CGM of two merging galaxies is less well
  understood. In this work, we present hydrodynamic simulations of a controlled
  galaxy merger, roughly resembling a merger the Milky Way experienced early in
  its history. Unsurprisingly, the CGM of the satellite galaxy is stripped early
  in the merger -- mostly during its first pericentric passage (check). This has
  the effect of stimulating the accretion of gas from the host's CGM onto its
  disk. This occurs due to two effects: (1) Cold gas from the satellite's CGM
  mixes with gas in the host's CGM and cools it to a regime where cooling is
  more efficient, thus reducing the gas' thermal pressure support. (2) The
  satellite deepens the potential well of the host galaxy, reducing its
  free-fall time. These effects combine to enhance the accretion of gas onto the
  host's disk. In our setup (for which there is significant uncertainty), the
  bulk amount of gas accreted on the disk can increase by a factor of $\sim2$
  (\textcolor{red}{checl}).
\end{abstract}

>>>>

\documentclass[linenumbers, twocolumn]{aastex631}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{newtxtext,newtxmath}
\usepackage{hyperref}

@@

\newcommand{\Msun}{\ensuremath{M_{\odot}}}
\newcommand{\Gyr}{\ensuremath{\textrm{Gyr}}}
\newcommand{\Myr}{\ensuremath{\textrm{Myr}}}
\newcommand{\yr}{\ensuremath{\textrm{yr}}}
\newcommand{\kpc}{\ensuremath{\textrm{kpc}}}
\newcommand{\pc}{\ensuremath{\textrm{pc}}}
\newcommand{\tocite}{\textcolor{blue}{cite}}
\newcommand{\FeH}{\ensuremath{[\textrm{Fe}/\textrm{H}]}}
\newcommand{\MgFe}{\ensuremath{[\textrm{Mg}/\textrm{Fe}]}}
\newcommand{\alphaFe}{\ensuremath{[\alpha/\textrm{Fe}]}}

\newcommand{\red}[1]{\textcolor{red}{#1}}

@@

\title{Rising from the Ashes: How the Milky Way Got Its Scars}

@@

@@

\author{et al}

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
  Stars are thought to inherit the elemental abundances of their birth cloud and, for the most part, to not change their surface abundances over time. Stellar surface abdundances are, therefore, a promising avenue to probe the time evolution of the abundance distribution of the Galaxy's gas phase. A particularly useful compression of the high-dimensional abundance plane is to consider the distribution of $\alpha$ elements for a given total metallicity, usually tracked by iron. It is well-known that this distribution of $\alpha$ is bimodal, for which there is a growing consensus that the low-$\alpha$ sequence diverges from the high-$\alpha$ sequence as a result of a merger. In this work, we propose the phoenix hypothesis: the bimodality is caused by a brief ($\sim300\,\Myr$) period of quiescent star formation, possibly preceded by a starburst. The bimodality is a natural consequence of stellar populations enriching the Galactic disk during a period in which no stars are forming. Our proposal is consistent with a merger, but it is agnostic to the exact mechanism by which the quiescent period arises. Our proposal predicts no overlap in age between the high- and low-$\alpha$ sequence at a given birth radius.
\end{abstract}
